---
title: "Rock Pool Temperature Model"
author: "Andy"
date: "12/7/2021"
output:
  html_document:
    df_print: paged
---

```{r, echo = FALSE, warning = FALSE}
library(ggplot2)
library(cowplot)
library(GGally)
library(AICcmodavg)
library(dplyr)
library(reshape2)
library(kimisc)
library(glmmTMB)
library(performance)
library(MuMIn)
library(prediction)
library(car)

temponly.df <- read.csv("temperature_data.csv")
abiotic.df <- read.csv("abiotic_data.csv")
temp.df <- merge(temponly.df, abiotic.df)
temp.df$Date <- as.factor(temp.df$Date)
```

# Histograms

First, let's take a look at some of the data and explore it for correlations.

## Temperature Metrics

```{r, echo = FALSE, warning = FALSE}
max.hist <- ggplot(temp.df, aes(x = MaxWTemp_C)) +
  geom_histogram(binwidth = 2, colour = "black", fill = "grey80") +  
  theme_classic( base_size = 12, base_line_size = 1 ) + 
  scale_y_continuous( expand = c(0, 0), limits = c(0, 60) ) +
  scale_x_continuous( limits = c(15, 45)) +
  xlab("Max Temperature (°C)") +
  ylab("Frequency") +
  theme( panel.border = element_rect( color = "black", fill = NA, size = 0.75 ),
         legend.position = "none",
         aspect.ratio = 1)


min.hist <- ggplot(temp.df, aes(x = MinWTemp_C)) +
  geom_histogram(binwidth = 2, colour = "black", fill = "grey80") +  
  theme_classic( base_size = 12, base_line_size = 1 ) + 
  scale_y_continuous( expand = c(0, 0), limits = c(0, 60) ) +
  scale_x_continuous( limits = c(15, 45)) +
  xlab("Min Temperature (°C)") +
  ylab("Frequency") +
  theme( panel.border = element_rect( color = "black", fill = NA, size = 0.75 ),
         legend.position = "none",
         aspect.ratio = 1)



# Across pool variation
aggregate(temp.df$MaxWTemp_C, by = list(temp.df$Date), FUN = max)
aggregate(temp.df$MaxWTemp_C, by = list(temp.df$Date), FUN = min)
maxtemp_mean <- aggregate(temp.df$MaxWTemp_C, by = list(temp.df$Date), FUN = mean)
maxtemp_sd <- aggregate(temp.df$MaxWTemp_C, by = list(temp.df$Date), FUN = sd)
maxtemp_se <- maxtemp_sd$x/sqrt(length(temp.df$MaxWTemp_C))

aggregate(temp.df$MinWTemp_C, by = list(temp.df$Date), FUN = max)
aggregate(temp.df$MinWTemp_C, by = list(temp.df$Date), FUN = min)
aggregate(temp.df$MinWTemp_C, by = list(temp.df$Date), FUN = max) - aggregate(temp.df$MinWTemp_C, by = list(temp.df$Date), FUN = min)
mintemp_mean <- aggregate(temp.df$MinWTemp_C, by = list(temp.df$Date), FUN = mean)
mintemp_sd <- aggregate(temp.df$MinWTemp_C, by = list(temp.df$Date), FUN = sd)
mintemp_se <- mintemp_sd$x/sqrt(length(temp.df$MinWTemp_C))

temp.df$temp_range <-  temp.df$MaxWTemp_C - temp.df$MinWTemp_C
cor(temp.df$MaxWTemp_C, temp.df$cvWTemp_C)
cor(temp.df$MinWTemp_C, temp.df$temp_range)

cv.hist <- ggplot(temp.df, aes(x = temp_range)) +
  geom_histogram(binwidth = 2, colour = "black", fill = "grey80") +  
  theme_classic( base_size = 12, base_line_size = 1 ) + 
  scale_y_continuous( expand = c(0, 0) ) +
  xlab("CV of Temperature") +
  ylab("Frequency") +
  theme( panel.border = element_rect( color = "black", fill = NA, size = 0.75 ),
         legend.position = "none",
         aspect.ratio = 1)

Fig2.plot <- plot_grid( max.hist, min.hist, cv.hist,
                        labels = c("a)", "b)", "c)"),
                        label_x = 0.32,
                        nrow = 3,
                        align = "hv" )


# ggsave( "../figs/Fig2_panels.png",
#         plot = Fig2.plot,
#         units = c("mm"),
#         dpi = 300 )


# Within pool variation
mean(temp.df$temp_range)
sd(temp.df$temp_range)/sqrt(length(temp.df$temp_range))

mintemp_mean <- aggregate(temp.df$MinWTemp_C, by = list(temp.df$Date), FUN = mean)
mintemp_sd <- aggregate(temp.df$MinWTemp_C, by = list(temp.df$Date), FUN = sd)
mintemp_cv <- mintemp_mean/mintemp_sd
mintemp_cv
```


## Applying Transformations

Rescaling and Z-scores for everything.

```{r, warning = FALSE}
temp.df$DistRC_m <- as.numeric(temp.df$DistRC_m)

temp.df$Depth_cm <- as.numeric(temp.df$Depth_cm)
temp.df$Depth_m <- temp.df$Depth_cm/100

temp.df$SurfArea_cm2 <- as.numeric(temp.df$SurfArea_cm2)
temp.df$SurfArea_m2 <- temp.df$SurfArea_cm2/10000

temp.df$Volume_cm3 <- as.numeric(temp.df$Volume_cm3)
temp.df$Volume_m3 <- temp.df$Volume_cm3/1000000

temp.df$Pct_Shaded <- as.numeric(temp.df$Pct_Shaded)
temp.df$Pct_Shaded <- temp.df$Pct_Shaded/100

temp.df$DistRC_Z <- (temp.df$DistRC_m - mean(temp.df$DistRC_m))/sd(temp.df$DistRC_m)
temp.df$Depth_Z <- (temp.df$Depth_cm - mean(temp.df$Depth_cm))/sd(temp.df$Depth_cm)
temp.df$SurfArea_Z <- (temp.df$SurfArea_cm2 - mean(temp.df$SurfArea_cm2))/sd(temp.df$SurfArea_cm2)
temp.df$Volume_Z <- (temp.df$Volume_cm3 - mean(temp.df$Volume_cm3))/sd(temp.df$Volume_cm3)
temp.df$Pct_Shaded_Z <- (temp.df$Pct_Shaded - mean(temp.df$Pct_Shaded))/sd(temp.df$Pct_Shaded)
temp.df$MaxRTemp_Z <- (temp.df$MaxRTemp_C - mean(temp.df$MaxRTemp_C))/sd(temp.df$MaxRTemp_C)
temp.df$MaxATemp_Z <- (temp.df$MaxATemp_C - mean(temp.df$MaxATemp_C))/sd(temp.df$MaxATemp_C)
```


# Correlation Plots

```{r, echo = FALSE, warning = FALSE}
temp2.df <- subset(temp.df, select = c("MaxWTemp_C", "MaxATemp_Z", "MaxRTemp_Z", "SurfArea_Z", "Depth_Z", "Pct_Shaded_Z", "DistRC_Z"))
# ggpairs(data = temp2.df)
```

Area and depth look like good predictors, as does maximum river temperature and shade. Oddly, there is also some colinearity going on with some of our predictor variables, too (e.g., area x depth, shade x depth).

# Max Temperature Modeling

Let's try making a basic GLMM using these variables, with area, depth, shade, and river temp as fixed effects and pool ID as a random effect. We'll take a stepwise approach to model selection.

```{r, echo = FALSE, results = "hide", warning = FALSE}
temp.df$DistRC_Z <- NULL
temp.df$Notes <- NULL

maxtempfull.mod <- glmmTMB(MaxWTemp_C ~ Depth_Z * SurfArea_Z * Pct_Shaded_Z + MaxRTemp_Z + (1 | Pool_ID), data = temp.df, na.action = "na.fail" )
maxtemp.dredge <- dredge(maxtempfull.mod) # Only one model is within dAIC of 2.0
maxtempfinal.mod <- get.models(maxtemp.dredge, subset = delta <= 2) # No model averaging needed


# Generate summary stats, save model
check_collinearity(maxtempfinal.mod[[1]]) 
summary(maxtempfinal.mod[[1]])
confint(maxtempfinal.mod[[1]])
r2(maxtempfinal.mod[[1]]) 

# write.csv(maxtemp.dredge, file = "../temperature/MaxTemp_aic.csv")
# saveRDS(maxtemp.mod_avg, file = "BelleRP_MaxTemp.rds")
```


## Predicting from the Model

The next step will be to challenge the model (and ourselves) a bit. Can we simulate a day on which the river temperature is 25°C, as an example, and predict temperatures for the whole system?

```{r, echo = FALSE, warning = FALSE}
# Grab and restructure the abiotic data and z score the necessary components
testdata.df <- read.csv("abiotic_data.csv")
testdata.df$Depth_cm <- as.numeric(testdata.df$Depth_cm)
testdata.df$Pct_Shaded <- as.numeric(testdata.df$Pct_Shaded)
testdata.df$SurfArea_cm2 <- as.numeric(testdata.df$SurfArea_cm2)
testdata.df$Pool_ID <- as.factor(testdata.df$Pool_ID)
testdata.df$MaxRTemp_Z <- rep(0, nrow(testdata.df))
testdata.df$Pct_Shaded <- testdata.df$Pct_Shaded/100
testdata.df$Depth_Z <- (testdata.df$Depth_cm - mean(testdata.df$Depth_cm, na.rm = TRUE))/sd(testdata.df$Depth_cm, na.rm = TRUE)
testdata.df$Pct_Shaded_Z <- (testdata.df$Pct_Shaded - mean(testdata.df$Pct_Shaded, na.rm = TRUE))/sd(testdata.df$Pct_Shaded, na.rm = TRUE)
testdata.df$SurfArea_Z <- (testdata.df$SurfArea_cm2 - mean(testdata.df$SurfArea_cm2, na.rm = TRUE))/sd(testdata.df$SurfArea_cm2, na.rm = TRUE)

# Remove NAs
testdata.df <- testdata.df[!is.na(testdata.df$Depth_Z),]
testdata.df <- testdata.df[!is.na(testdata.df$Pct_Shaded_Z),]
testdata.df <- testdata.df[!is.na(testdata.df$SurfArea_cm2),]

# Predict max temps from the averaged model
predict2.df <- predict(maxtempfinal.mod[[1]], newdata = testdata.df, allow.new.levels = TRUE, se.fit = TRUE, na.rm = TRUE)
predicted.df <- cbind(testdata.df, predict2.df)
names(predicted.df)[names(predicted.df) == 'fit'] <- 'MaxTemp_Predicted_C'
names(predicted.df)[names(predicted.df) == 'se.fit'] <- 'MaxTemp_SE'
predicted.df$MaxTemp_Z <- (predicted.df$MaxTemp_Predicted_C - mean(predicted.df$MaxTemp_Predicted_C))/sd(predicted.df$MaxTemp_Predicted_C)

# Save the prediced max temps
# write.csv(predicted.df, file = "../temperature/MaxTemp_predicted.csv")
```


# Min Temperature Model

Some subsequent models, for minimum temperatures and the coefficient of variation.

```{r}
mintempfull.mod <- glmmTMB(MinWTemp_C ~ Depth_Z * SurfArea_Z * Pct_Shaded_Z + MaxRTemp_Z, data = temp.df, na.action = "na.fail" ) 
mintemp.dredge <- dredge(mintempfull.mod) # Won't run with pool-level random effect
mintempfinal.mod <- get.models(mintemp.dredge, subset = delta <= 2) # This would need model averaging, as four models are tied for top


# Generate summary stats, save model
check_collinearity(mintempfinal.mod[[1]]) 
summary(mintempfinal.mod[[1]])
confint(mintempfinal.mod[[1]])
r2(mintempfinal.mod[[1]]) 

# write.csv(maxtemp.dredge, file = "../temperature/MaxTemp_aic.csv")
# saveRDS(maxtemp.mod_avg, file = "BelleRP_MaxTemp.rds")
```

# CV Temperature Model

```{r}
cvtempfull.mod <- glmmTMB(cvWTemp_C ~ Depth_Z * SurfArea_Z * Pct_Shaded_Z + MaxRTemp_Z + (1 | Pool_ID), data = temp.df, na.action = "na.fail" ) 
cvtemp.dredge <- dredge(cvtempfull.mod) # Won't run with pool-level random effect
cvtempfinal.mod <- get.models(cvtemp.dredge, subset = delta <= 2) # This would need model averaging, as four models are tied for top


# Generate summary stats, save model
check_collinearity(mintempfinal.mod[[1]]) 
summary(mintempfinal.mod[[1]])
confint(mintempfinal.mod[[1]])
r2(mintempfinal.mod[[1]]) 

# write.csv(maxtemp.dredge, file = "../temperature/MaxTemp_aic.csv")
# saveRDS(maxtemp.mod_avg, file = "BelleRP_MaxTemp.rds")
```
