---
title: "Abundance Modeling"
author: "Andy"
date: "3/14/2022"
output: html_document
---

# Models of Mosquito Abundance

```{r, echo = FALSE, warnings = FALSE, message = FALSE, include = FALSE}
library(glmmTMB)
library(DHARMa)
library(dotwhisker)
library(broom)
library(broom.mixed)
library(ggeffects)
library(AICcmodavg)
library(performance)
library(cowplot)
library(MuMIn)
```

```{r, echo = FALSE, warnings = FALSE, message = FALSE}
abundance.df <- read.csv("abundance_data.csv")
abundance.df$Pool_ID <- as.factor(abundance.df$Pool_ID)
abundance.df$Date <- as.factor(abundance.df$Date)

abiotic.df <- read.csv( "../temperature/MaxTemp_predicted.csv" )
abiotic.df$Pool_ID <- as.factor(abiotic.df$Pool_ID)

abundance.df <- merge(abundance.df, abiotic.df)
abundance.df$Skimmer_Z <- ( abundance.df$Skimmer_Dragonfly - mean( abundance.df$Skimmer_Dragonfly ) )/sd( abundance.df$Skimmer_Dragonfly )
abundance.df$Days_Between_Z <- ( abundance.df$Days_Between_Flood_Sampling - mean( abundance.df$Days_Between_Flood_Sampling ) )/sd( abundance.df$Days_Between_Flood_Sampling )
abundance.df$drgn_presence <- ifelse(abundance.df$Skimmer_Dragonfly > 0, 'Present', 'Absent')
abundance.df$drgn_presence <- as.factor(abundance.df$drgn_presence)
```

## Model Family
### Standard Poisson GLMM

```{r, echo = FALSE}
mosq_poisson <- glmmTMB(Mosquito ~ Skimmer_Z * MaxTemp_Z + (1 | Pool_ID), family = poisson(), data = abundance.df )
summary(mosq_poisson)
testDispersion(mosq_poisson) # It's overdispersed
testZeroInflation(mosq_poisson) # And zero-inflated
```


### Negative Binomial GLMM

```{r, echo = FALSE}
mosq_nbinom2 <- glmmTMB(Mosquito ~ Skimmer_Z * MaxTemp_Z + (1 | Pool_ID), family = nbinom2(), data = abundance.df )
summary(mosq_nbinom2)
testDispersion(mosq_nbinom2)
testZeroInflation(mosq_nbinom2)

# nbinom1 had a similar AIC (slightly lower) but an insanely high dispersion parameter
```


### Zero-Inflated Poisson GLMM

```{r, echo = FALSE}
mosq_trunc_poisson <- glmmTMB(Mosquito ~ Skimmer_Z * MaxTemp_Z + (1 | Pool_ID), ziformula = ~., family = truncated_poisson, data = abundance.df )
summary(mosq_trunc_poisson)
testDispersion(mosq_trunc_poisson)
testZeroInflation(mosq_trunc_poisson)
```


### Zero-Inflated Negative Binomial GLMM

```{r, echo = FALSE}
mosq_trunc_nbinom2 <- glmmTMB(Mosquito ~ Skimmer_Z * MaxTemp_Z + (1 | Pool_ID), ziformula = ~., family = truncated_nbinom2, data = abundance.df )
summary(mosq_trunc_nbinom2)
testDispersion(mosq_trunc_nbinom2)
testZeroInflation(mosq_trunc_nbinom2) 

# Ditto here
```

The truncated negative binomial model seems to work the best (lowest AIC), and indicates a positive effect of temperature on mosquito abundance, a negative effect of dragonflies, and a positive interaction term. This suggests that mosquitoes are more abundant in warmer pools, less abundant where dragonflies are present, but temperature may mitigate this effect somewhat.


## Models Including Flooding and Other Variables

```{r, echo = FALSE}
# This limits the analysis to temperatures below where they stopped co-occurring
abundance.df <- abundance.df[which(abundance.df$MaxTemp_Predicted_C <35),]
abundance.df$MaxTemp_Z <- (abundance.df$MaxTemp_Predicted_C - mean(abundance.df$MaxTemp_Predicted_C))/sd(abundance.df$MaxTemp_Predicted_C)

abundance.fullmod <- glmmTMB(Mosquito ~ MaxTemp_Z * drgn_presence * Days_Between_Z + (1 | Date), ziformula = ~ drgn_presence + (1 | Date), family = truncated_nbinom2(), data = abundance.df, na.action = "na.fail")
abundance.dredge <- dredge(abundance.fullmod)
abundance.finalmod <- get.models(abundance.dredge, subset = delta <= 2) # Two top models, one with flooding and one without
abundance.avgmod <- model.avg(abundance.dredge, subset = delta <= 2) # Apply model averaging

# Generate summary stats, save model
summary(abundance.avgmod)
confint(abundance.avgmod)
r2(abundance.avgmod) # As I suspected, r^2 values can't be calculated for these types of models
r2(abundance.finalmod[[1]]) # We can report the individual models' r-squareds and the weights
r2(abundance.finalmod[[2]])

# write.csv(abundance.dredge, file = "../temperature/Abundance_aic.csv")

```



```{r}
int_effect <- ggpredict(mosq.cand.models[[4]], terms = c("MaxTemp_Z [all]", "drgn_presence"), ci.lvl = 0.95, type = "fe.zi")
int_effect2 <- ggpredict(mosq.cand.models[[4]], terms = c("drgn_presence"), ci.lvl = 0.95, type = "zi.prob") # Remember, these are pr(ABSENCE)
int_effect$MaxTemp <- int_effect$x * sd(abundance.df$MaxTemp_Predicted_C) + mean(abundance.df$MaxTemp_Predicted_C) 
int_effect$drgn_presence <- int_effect$group
int_effect2$std.error_tf <- (int_effect2$conf.high - int_effect2$predicted)/1.96
int_effect2$predicted <- 1 - int_effect2$predicted
int_effect2$x <- as.factor(int_effect2$x)
nonzero.df <- abundance.df[ which(abundance.df$Mosquito > 0), ] # Grab nonzero observations

int_effect.plot1 <- ggplot(int_effect2, aes(x = x, y = predicted)) +
  geom_bar( stat = "identity", aes( fill = x ) ) +
  geom_errorbar( aes( ymin = predicted - std.error_tf, ymax = predicted + std.error_tf ), width = .2 ) +
  scale_y_continuous( expand = c(0, 0) ) +
  coord_cartesian(ylim = c(0, 1)) +
  xlab("Predators") +
  ylab("Probability of Prey Presence") +
  scale_fill_manual( values = c( "#FFC107", "#1E88E5" ) ) +
  theme_classic( base_size = 10, base_line_size = 0.1 ) +
  theme( panel.border = element_rect( color = "black", fill = NA, size = 0.75 ),
         legend.position = "none",
         aspect.ratio = 1)


int_effect.plot2 <- ggplot( int_effect, aes( MaxTemp, predicted + 1, colour = drgn_presence ) ) +
  geom_line( size = 0.5 ) +
  geom_ribbon(aes( ymin = conf.low + 1, ymax = conf.high + 1, fill = drgn_presence ), alpha = 0.25, show.legend = F, colour = NA) +
  geom_point(nonzero.df, mapping = aes(x = MaxTemp_Predicted_C, y = Mosquito + 1 ), size = 1, alpha = 0.35 ) +
  theme_classic( base_size = 10, base_line_size = 0.1 ) +
  scale_y_log10( expand = c(0, 0) ) +
  scale_x_continuous( expand = c(0, 0) ) +
  coord_cartesian(xlim = c(23.92, 34.62)) +
  xlab("Max Temperature (°C)") +
  ylab("Prey Abundance + 1") +
  scale_colour_manual( name = "Predators", values = c( "#FFC107", "#1E88E5" ) ) +
  scale_fill_manual( name = "Predators", values = c( "#FFC107", "#1E88E5" ) ) +
  theme( panel.border = element_rect( color = "black", fill = NA, size = 0.75 ),
         legend.position = "right",
         aspect.ratio = 1)


int_effect_pres <- int_effect[which(int_effect$drgn_presence == "Present"), ]
int_effect_abs <- int_effect[which(int_effect$drgn_presence == "Absent"), ]
int_effect_pres$effect <- (int_effect_abs$predicted - int_effect_pres$predicted)/int_effect_abs$predicted
int_effect_pres$ci <- ((1/int_effect_abs$predicted)^2) * var(int_effect_pres$predicted) + ((int_effect_pres$predicted/(int_effect_abs$predicted^2))^2) * var(int_effect_abs$predicted)
int_effect_pres$ci <- sqrt(int_effect_pres$ci) * 1.96

int_effect.plot3 <- ggplot( int_effect_pres, aes( x = MaxTemp, y = effect ) ) +
  geom_line( size = 0.5 ) +
  geom_ribbon(aes( ymin = effect - ci, ymax = effect + ci ), alpha = 0.25, show.legend = F, colour = NA) +
  theme_classic( base_size = 10, base_line_size = 0.1 ) +
  scale_x_continuous( expand = c(0, 0) ) +
  scale_y_continuous( expand = c(0, 0) ) +
  coord_cartesian(xlim = c(23.92, 34.62), ylim = c(0, 2.2) ) +
  xlab("Max Temperature (°C)") +
  ylab("Proportional Difference") +
  scale_colour_discrete(name = "Predators") +
  theme( panel.border = element_rect( color = "black", fill = NA, size = 0.75 ),
         legend.position = "bottom",
         aspect.ratio = 1)

legend.plot <- get_legend(int_effect.plot2)
int_effect.plot2 <- int_effect.plot2 + theme( legend.position = "none" )

Fig6.plot <- plot_grid(int_effect.plot1, int_effect.plot2, int_effect.plot3, ncol = 1, align = c("v"), axis = c("l"), labels = c("a)", "b)", "c)" ), label_x = 0.275 )


ggsave("../abundance/Fig6.png", plot = Fig6.plot, units = c( "mm" ), dpi = 300, bg = "white" )
ggsave("../abundance/Fig6_legend.png", plot = legend.plot, units = c( "mm" ), dpi = 300, bg = "white" )
```


```{r}
## Landscape Level Predictions
# We'll do some predictions where T = current predicted, and T = current + 2.5
ambient.df <- predict(model.avg(abundance.dredge, subset = delta <= 2, fit = TRUE), newdata = abundance.df, type = "response", allow.new.levels = TRUE, se.fit = TRUE)
sum(ambient.df$fit) # mean estimate = 8621.5
sum(ambient.df$fit - ambient.df$se.fit) # low end = 4030.7
sum(ambient.df$fit + ambient.df$se.fit) # high end = 13212.3

abundance2.df <- abundance.df
abundance2.df$MaxTemp_Z <- abundance.df$MaxTemp_Z + (2.5)/sd(abundance.df$MaxTemp_Predicted_C)
warmed.df <- predict(model.avg(abundance.dredge, subset = delta <= 2, fit = TRUE), newdata = abundance2.df, type = "response", allow.new.levels = TRUE, se.fit = TRUE)
sum(warmed.df$fit) # mean estimate = 15674.0
sum(warmed.df$fit - warmed.df$se.fit) # low end = 6069.9
sum(warmed.df$fit + warmed.df$se.fit) # high end = 25278.1


# So, between 1.5 to 1.9x more mosquito production at T + 2.5C
```



# Models of Dragonfly Abundance

```{r, echo = FALSE}
dfly.fullmod <- glmmTMB(Skimmer_Dragonfly ~ MaxTemp_Z + Pct_Shaded_Z + Days_Between_Z + (1 | Date), ziformula = ~ Pct_Shaded_Z, family = truncated_nbinom2(), data = abundance.df, na.action = "na.fail")
dfly.dredge <- dredge(dfly.fullmod)
dfly.finalmod <- get.models(dfly.dredge, subset = delta <= 2) # 7 top models... holy hell
dfly.finalmod
dfly.avgmod <- model.avg(dfly.dredge, subset = delta <= 2) # Apply model averaging

# Generate summary stats, save model
summary(dfly.avgmod) # All that to say that they are simply less likely to be present in shaded pools
confint(dfly.avgmod)

# write.csv(dfly.dredge, file = "../temperature/dragonfly_aic.csv")
```